Finite element analysis ofmulti-dimensional and simplifiedmodels for beams and plates

### 2023-11-23 files/Chapter3/femconvergence.tex
chapter 4

\subsection{Estimating the eigenvalues.}
\textbf{Rayleigh quotient}
\begin{equation*}
	R(v) = \frac{b(v,v)}{(v,v)} \ \text { for } v \in V.
\end{equation*} \label{sym:Rayleigh}

@@

Then consider the subspace $S_j$ where
\begin{equation*}
	S_j = PE_j \ \text{ for } j = 1,2,...,m.
\end{equation*} The elements $Py_i$ are the projections of the eigenfunctions $u_i$ into the space $S^h$. These projections $Py_i$ are not necessarily equal to $u^h_j \in S^h$, but it can be shown that they are close.

@@

@@

The first step to obtain estimates for the eigenvalues, it to show that the elements of $B_m$ are linearly independent.

\newtheorem{Prop_2}[Prop_1]{Proposition} \label{Prop_2}
\begin{Prop_2}
	$\lambda^{h}_{m} \leq \max R(Pu) \ \text{ for } u \in B_{m}$\\
\end{Prop_2}
\begin{proof}
	Since $\dim S_{m} = m$, following from the minmax principle
	\begin{equation*}
		\lambda_m^h \leq \max R(v) \ \text{ for } v \in S_m.
	\end{equation*}

	Take an arbitrary nonzero $v \in S_m$. Then there exists a $Py \in E_m$ such that $v = Py$.\\

	Now we take an arbitrary $v \in S_{m}$, $v \neq 0$. Then there exists a $u \in E_{m}$ such that $Py = v$. This $Py$ is the projection into $S_m$ of some $u \in E_m$ (which is also $\displaystyle \frac{1}{||u||}u \in B_m$).\\

	Next a linearity property for $R$ can be proven. 
	\begin{eqnarray*}
	R(\frac{1}{||u||}u) &=& \frac{b\left(\frac{1}{||u||}u,\frac{1}{||u||}u\right)}{\left(\frac{1}{||u||}u,\frac{1}{||u||}u\right)},\\
						&=& \frac{b(u,u)}{(u,u)},\\
						&=& R(u).
	\end{eqnarray*}
	So finally,
	\begin{eqnarray*}
	\lambda_{m}^{h} &\leq & \max R(v) \ \text{ for } \ v \in S_{m},\\
						&=& \max R(Pu) \ \text{ for } \ u \in E_{m},\\
						&=& \max R(Pu) \ \text{ for } \ u \in B_{m}.
	\end{eqnarray*}
\end{proof}

Pick any $i,j \in \mathbb{N}$ such that $i,j \leq m$. Let $v_{i},v_{j} \in V$ be arbitrary, then
\begin{eqnarray*}
	b(u_{i},u_{i}) &=& \lambda_{i}( u_{i},u_{i}),\\
	b(u_{j},u_{j}) &=& \lambda_{j}( u_{j},u_{j}).
\end{eqnarray*}
Now pick $u_{i} = u_{j}$ and $u_{j} = u_{i}$. Then
\begin{eqnarray*}
	b(u_{i},u_{j}) &=& \lambda_{i}( u_{i},u_{j}),\\
	b(u_{j},u_{i}) &=& \lambda_{j}( u_{j},u_{i}).
\end{eqnarray*}
Then using the symmetry of $b(\cdot,\cdot)$ and $( \cdot, \cdot )$, and subtracting,
\begin{eqnarray*}
	0 &=& (\lambda_{i} - \lambda_{j})( u_{i}, u_{j} )
\end{eqnarray*}
So if $i \neq j$ then $\lambda_{i} \neq \lambda_{j}$.\\

Therefore $u_{i}$ and $u_{j}$ must be orthogonal. And as mentioned previously, $||u|| = 1$.

\newtheorem{Lem_1}{Lemma} \label{Lem_1}
\begin{Lem_1}
	$\displaystyle \lambda_{m}^{h} \leq \frac{\lambda_{m}}{u_{m}^{h}}$
\end{Lem_1}
\begin{proof}
	Consider the linearity of the bilinear form $b$, and fact that any $u \in E_m$ can be expressed as a linear combination $u = \sum_{i=1}^{m} c_{i}u_{i}$. Then
	\begin{eqnarray*}
	b(u,u) &=& b\left(\sum_{i=1}^{m} c_{i}u_{i},\sum_{j=1}^{m} c_{j}u_{j}\right),\\
			&=& \sum_{i=1}^{m} c_{i}\sum_{j=1}^{m} c_{j} b(u_{i},u_{j}).
	\end{eqnarray*}

@@

	Using the Rayleigh quotient, and the definition of $\mu_{m}^{h}$, 
	\begin{eqnarray*}
		R(Pu) &=& \frac{b(Pu,Pu)}{(Pu,Pu)},\\
			&=& \frac{b(Pu,Pu)}{||Pu||^{2}},\\
			&\leq & \frac{\lambda_{m}}{\mu_{m}^{h}}.
	\end{eqnarray*}

@@

Following Lemma \ref{Lem_1}, and since $\lambda_{i}^{h} \geq \lambda_{i}$ it follows that $0 < \mu_{m}^{h} \leq 1$. It is now possible to define the error estimate as given in \cite{SF73}:
\begin{eqnarray*}
	\sigma_{m}^{h} = 1 - \mu_{m}^{h}.
\end{eqnarray*}

\newtheorem{Cor_1}{Corollary}
\begin{Cor_1}
	$0 \leq \sigma_{m}^{h} < 1$ and $\lambda_{m}^{h} - \lambda_{m} \leq \lambda_{m}^{h}\sigma_{m}^{h}$
\end{Cor_1}
\begin{proof}
	Starting with the result of Lemma \ref{Lem_1},
	\begin{eqnarray*}
		\lambda_{m}^{h} & \leq & \frac{\lambda_{m}}{\mu_{m}^{h}}\\
		\lambda_{m}^{h}\mu_{m}^{h}& \leq & \lambda_{m} \\
		-\lambda_{m}& \leq & -\lambda_{m}^{h}\mu_{m}^{h} \\
		\lambda_{m}^{h} -\lambda_{m}& \leq & \lambda_{m}^{h} -\lambda_{m}^{h}\mu_{m}^{h}\\
		\lambda_{m}^{h} -\lambda_{m}& \leq & \lambda_{m}^{h}\sigma_{m}^{h}
		\end{eqnarray*}
\end{proof}

This corollary give a error estimate for the eigenvalues. To prove the convergence of the eigenvalues, it is necessary to prove that the error estimate $\sigma_{m}^{h}$ converges to zero as $h \rightarrow 0$.

\newtheorem{Prop_3}[Prop_1]{Proposition} \label{Prop_3}
\begin{Prop_3}
	$\sigma_{m}^{h} = \max\left\{ 2( u,u-Pu )-||u-Pu||^{2} \ | \ u \in B_{m} \right\}$
\end{Prop_3}
\begin{proof}
	Let $u \in B_{m}$. Then
	\begin{eqnarray*}
		||u - Pu||^{2} &=& ( u - Pu, u - Pu ), \\
						&=& ( u, u ) - 2 ( u, Pu ) + ( Pu, Pu ), \\
						&=& 2( u, u ) - 2 ( u, Pu ) + ( Pu, Pu ) - ( u, u ),\\
						&=& 2( u, u - Pu ) + ( Pu, Pu ) - ( u, u ).\\
	\end{eqnarray*}
	Rewriting gives
	\begin{eqnarray*}
		( u, u ) - ( Pu, Pu )  & = & 2( u, u - Pu ) - ||u - Pu||^{2}.
	\end{eqnarray*}

	Since $u \in B_{m}$, $||u||^{2} = 1$. So then
	\begin{eqnarray*}
		1 - ||Pu||^{2}  & = & 2( u, u - Pu ) - ||u - Pu||^{2}.
	\end{eqnarray*}

	On the right hand side, $1 - ||Pu||^{2} \leq 1 - \mu_{m}^{h} = \sigma_{m}^{h}$ for all $u \in B_{m}$. So then it must be that
	\begin{eqnarray*}
	\sigma_{m}^{h} = \max\left\{ 2( u,u-Pu )-||u-Pu||^{2} \ | \ u \in B_{m} \right \}
	\end{eqnarray*}
\end{proof}

@@

\newtheorem{Prop_4}[Prop_1]{Proposition} \label{Prop_4}
\begin{Prop_4}
	For any $u \in E_{m}$
		\begin{eqnarray*}
		( u, u - Pu ) = b(u^{*} - Pu^{*}, u -Pu)
		\end{eqnarray*}
\end{Prop_4}
\begin{proof}
	For any $i = 1,2,...,m$,
	\begin{eqnarray*}
	\lambda_{i}( u_{i},u-Pu ) &=&  b(u_{i}, u-Pu),\\
								&=& b(u_{i}, u-Pu) - b(u-Pu,Pu_{i}) \ \textrm{ (Rayleigh-Ritz Projection)},\\
								&=&  b(u_{i}, u-Pu) - b(Pu_{i},u-Pu),\\
								&=&  b(u_{i}-Pu_{i}, u-Pu).
	\end{eqnarray*}
	Multiplying by $c_{i}\lambda_{i}^{-1}$ and summation over i gives:
	\begin{eqnarray*}
	\sum_{i=1}^{m} c_{i}\lambda_{i}^{-1}\lambda_{i}( u_{i},u-Pu ) &=& \sum_{i=1}^{m} c_{i}\lambda_{i}^{-1}b(u_{i}-Pu_{i}, u-Pu),\\
								&=& b(\sum_{i=1}^{m} c_{i}\lambda_{i}^{-1}u_{i}-\sum_{i=1}^{m} c_{i}\lambda_{i}^{-1}Pu_{i}, u-Pu),\\
										&=& b(u^{*}-Pu^{*}, u-Pu).
	\end{eqnarray*}
	Therefore $( u,u-Pu ) = b(u^{*}-Pu^{*}, u-Pu)$.
\end{proof}

\newtheorem{Lem_2}[Lem_1]{Lemma} \label{Lem_2}
\begin{Lem_2}
	$\sigma_{m}^{h} \leq \max \left\{2||u^{*}- Pu^{*}|| ||u-Pu|| \ | \ u \in B_{m} \right\}$
\end{Lem_2}
\begin{proof}
	From Proposition \ref{Prop_3},
	\begin{eqnarray*}
		\sigma_{m}^{h} & = & \max\left\{ 2( u,u-Pu )-||u-Pu||^{2} \ | \ u \in B_{m} \right\}, \\
					& \leq & \max\left\{ 2( u,u-Pu ) \ | \ u \in B_{m} \right\}. \\
	\end{eqnarray*}

@@

	From the Approximation Theorem, is follows that
	\begin{eqnarray*}
		||u - \Pi u|| \leq Ch^{k}||u^{(k)}||
	\end{eqnarray*}

@@

\newtheorem{Lem_3}[Lem_1]{Lemma} \label{Lem_3}
\begin{Lem_3}
	For any $\epsilon >0$ there exists a $\delta > 0$ such that
	\begin{eqnarray*}
	\sigma_{m}^{h} < \epsilon \ \textrm{ if } \ h < \delta
	\end{eqnarray*}
\end{Lem_3}
\begin{proof}
	For any $\epsilon > 0$ there exists a $\delta > 0$ such that if $h<\delta$, then
	\begin{eqnarray*}
	||u-Pu|| < \epsilon \ \textrm{ for each } \ u \in B_{m}
	\end{eqnarray*}
	This result, together with Lemma \ref{Lem_2} and Proposition \ref{Prop_5} gives the result.
\end{proof}

\newtheorem{Lem_4}[Lem_1]{Lemma} \label{Lem_4}
\begin{Lem_4}
	There exists a $\delta > 0$ such that for $h < \delta$
	\begin{eqnarray*}
	\lambda_{m}^{h} - \lambda_{m} \leq 2\lambda_{m}\sigma_{m}^{h}
	\end{eqnarray*}
\end{Lem_4}
\begin{proof}
	Using Lemma \ref{Lem_3}, choose $\delta$ such that $\sigma_{m}^{h} < \frac{1}{2}$. Then by Lemma \ref{Lem_1} gives that $\lambda_{m}^{h} < 2\lambda_{m}$.\\

	So $\lambda_{m}^{h} - \lambda_{m} \leq 2\lambda_{m}\sigma_{m}^{h}$.
\end{proof}

@@

\newtheorem{Lem_5}[Lem_1]{Lemma} \label{Lem_5}
\begin{Lem_5}
	\begin{eqnarray*}
		b(u_{m}-u_{m}^{h},u_{m}-u_{m}^{h}) &=& \lambda_{m}( u_{m}-u_{m}^{h},u_{m}-u_{m}^{h} ) + \lambda_{m}^{h} - \lambda_{m}
		\end{eqnarray*}
\end{Lem_5}
\begin{proof}
	\begin{eqnarray*}
		b(u_{m}-u_{m}^{h},u_{m}-u_{m}^{h}) &=& b(u_{m},u_{m}) - 2b(u_{m},u^{h}_{m}) + b(u^{h}_{m},u^{h}_{m}) \\
										&=& \lambda_{m} ( u_{m}, u_{m} ) - 2\lambda_{m} ( u_{m}, u^{h}_{m} ) + \lambda_{m}^{h}( u_{m}^{h},u_{m}^{h} )\\
										&=&  \lambda_{m} - 2\lambda_{m} ( u_{m}, u^{h}_{m} ) + \lambda_{m}^{h} \\
										&=& 2\lambda_{m} - 2\lambda_{m} ( u_{m}, u^{h}_{m} ) + \lambda_{m}^{h} - \lambda_{m}\\
										&=& \lambda_{m}( u_{m}-u_{m}^{h},u_{m}-u_{m}^{h}) + \lambda_{m}^{h} - \lambda_{m}
		\end{eqnarray*}
\end{proof}

It has been shown that the eigenvalues converge to the exact eigenvalues as $h \rightarrow 0$. So from this result, it only remains to show that $( u_{m}-u_{m}^{h},u_{m}-u_{m}^{h}) \rightarrow 0$ as $h \rightarrow 0$.

@@

\newtheorem{Lem_6}[Lem_1]{Lemma} \label{Lem_6}
\begin{Lem_6}
	For all m and j
	\begin{eqnarray*}
	(\lambda_{j}^{h} - \lambda_{m}) ( Pu_{m}, u_{j}^{h}) = \lambda_{m} ( u_{m}-Pu_{m},u_{j}^{h} )
	\end{eqnarray*}
\end{Lem_6}
\begin{proof}
	Since the term $\lambda_{m}( Pu,u^{h}_{j})$ appears on both sides of the equation, it is only required to show that
	\begin{eqnarray*}
		\lambda_{j}^{h}( Pu, u_{j}^{h} ) &=& \lambda_{m} ( u, u_{j}^{h} ).	
	\end{eqnarray*}
	Since both $u$ and $u_{j}^{h}$ are eigenfunctions, then
	\begin{eqnarray*}
		\lambda_{j}^{h}( Pu, u_{j}^{h} ) &=& b(Pu,u_{j}^{h})\\
		\lambda_{m} ( u, u_{j}^{h} ) &=& b(u,u_{j}^{h})
	\end{eqnarray*}

@@

The set $\left\{u_{1}^{h},u_{2}^{h},...,u_{N}^{h}\right\}$ forms an orthonormal basis for $S^{h}$. The projection $Pu_{m}$ can be written as:
\begin{eqnarray}
	Pu_{m} &=& \sum_{j=1}^{N} ( P u_{m} ,u_{j}^{h}) u_{j}^{h}. \label{CV1}
\end{eqnarray}

From Lemma \ref{Lem_6}, it follows that $( P_{m},u_{j}^{h} )$ is small if $\lambda_{m}^{h}$ is not close to $\lambda_{j}$. Therefore (\ref{CV1}) tells us that $Pu_{m}$ is close to $u_{m}^{h}$. The estimate for $Pu_{m} - u_{m}^{h}$ will follow from this result.

@@

To simplify the notation, let $\beta = (Pu_m,Pu_m^h)$.

@@

Using Lemma \ref{Lem_6}:
\begin{eqnarray*}
||Pu - \beta u_{m}^{h}||^{2} &=& \sum_{j\neq m} \left(\frac{\lambda_{m}}{|\lambda_{m} - \lambda_{j}^{h}|}\right)^{2} ( u_{m} - Pu_{m} ,u_{j}^{h})^{2},\\
				&\leq & \rho^{2} \sum_{j\neq m} ( u_{m} - Pu_{m} ,u_{j}^{h})^{2}, \\
				&\leq & \rho^{2} \sum_{j=1}^{N} ( u_{m} - Pu_{m} ,u_{j}^{h})^{2}, \\
				& = & \rho^{2} ||u_m - Pu_m||^{2}.\\
\end{eqnarray*}
\end{proof}
\end{comment}

>>>>

\subsection{Estimating the eigenvalues.} \label{sec:est}
\textbf{Rayleigh quotient}
\begin{equation}
	R(v) = \frac{b(v,v)}{c(v,v)} \ \text { for } v \in V. \label{Rayleigh}
\end{equation} \label{sym:Rayleigh}

@@

Then consider the subspace $S_j$ of $S^h$ where
\begin{equation*}
	S_j = PE_j \ \text{ for } j = 1,2,...,m.
\end{equation*} The elements $Py_i$ are the projections of the eigenfunctions $u_i$ into the space $S^h$. These projections $Py_i$ are not necessarily equal to $u^h_j \in S^h$, but it can be close. The situation is not simple. It is possible that $S_j$ is not a subspace of $S^h$. Assume that the dimension of $S^h$ is large enough

\vspace{20mm}

(It is possible that $Py_k = 0$ for large $k$.)

@@

The first step to obtain estimates for the eigenvalues, it to show that the elements of $B_m$ are linearly independent. In the first part we follow the approach in \cite{Zie2000} (A Computable Spectral Theorem - Martin Ziegler - 2000). The author introduced the quantity $\mu_m$.

 Recall the definition of the Rayleigh quotient R in \eqref{Rayleigh}.

\newtheorem{Prop_2}[Prop_1]{Proposition}
\begin{Prop_2}
	\label{Prop_2}
	$\lambda^{h}_{m} \leq \max R(Pu) \ \text{ for } u \in B_{m}$
\end{Prop_2}
\begin{proof}
	Since $\dim S_{m} = m$, following from the minmax principle
	\begin{equation*}
		\lambda_m^h \leq \max R(v) \ \text{ for } v \in S_m.
	\end{equation*}

	Take an arbitrary nonzero $v \in S_m$. Then there exists a $Py \in E_m$ such that $v = Py$.

	Now we take an arbitrary $v \in S_{m}$, $v \neq 0$. Then there exists a $u \in E_{m}$ such that $Py = v$. This $Py$ is the projection into $S_m$ of some $u \in E_m$ (which is also $\displaystyle \frac{1}{||u||}u \in B_m$).

	Next we show that $R(||u||^{-1}u) = R(u)$:

	\[ \frac{b\left(\frac{1}{||u||}u,\frac{1}{||u||}u\right)}{c\left(\frac{1}{||u||}u,\frac{1}{||u||}u\right)} = \frac{b(u,u)}{c(u,u)} = R(u). \]

	So finally,
	\begin{eqnarray*}
	\lambda_{m}^{h} &\leq & \max R(v) \ \text{ for } \ v \in S_{m},\\
						&=& \max R(Pu) \ \text{ for } \ u \in E_{m},\\
						&=& \max R(Pu) \ \text{ for } \ u \in B_{m}.
	\end{eqnarray*}
\end{proof}

Pick any $i,j \in \mathbb{N}$ such that $i,j \leq m$. Let $v_{i},v_{j} \in V$ be arbitrary, then
\begin{eqnarray*}
	b(u_{i},u_{i}) &=& \lambda_{i}c(u_{i},u_{i}),\\
	b(u_{j},u_{j}) &=& \lambda_{j}c(u_{j},u_{j}).
\end{eqnarray*}
Now pick $u_{i} = u_{j}$ and $u_{j} = u_{i}$. Then
\begin{eqnarray*}
	b(u_{i},u_{j}) &=& \lambda_{i}c(u_{i},u_{j}),\\
	b(u_{j},u_{i}) &=& \lambda_{j}c(u_{j},u_{i}).
\end{eqnarray*}
Then using the symmetry of $b(\cdot,\cdot)$ and $c( \cdot, \cdot )$, and subtracting,
\begin{eqnarray*}
	0 &=& (\lambda_{i} - \lambda_{j})c( u_{i}, u_{j} )
\end{eqnarray*}
So if $i \neq j$ then $\lambda_{i} \neq \lambda_{j}$. Therefore $u_{i}$ and $u_{j}$ must be orthogonal.

And as mentioned previously, $||u|| = 1$.

@@

\newtheorem{Lem_1}{Lemma} 
\begin{Lem_1}
	\label{Lem_1}
	$\displaystyle \lambda_{m}^{h} \leq \frac{\lambda_{m}}{\mu_{m}^{h}}$
\end{Lem_1}
\begin{proof}
	Consider the linearity of the bilinear form $b$, and fact that any $u \in E_m$ can be expressed as a linear combination $u = \sum_{i=1}^{m} c_{i}u_{i}$. Then
	\begin{eqnarray*}
	b(u,u) &=& b\left(\sum_{i=1}^{m} c_{i}u_{i},\sum_{j=1}^{m} c_{j}u_{j}\right),\\
			&=& \sum_{i=1}^{m} c_{i}\sum_{j=1}^{m} c_{j} b(u_{i},u_{j}).
	\end{eqnarray*}

@@

	Using the Rayleigh quotient, and the definition of $\mu_{m}^{h}$, 
	\begin{eqnarray*}
		R(Pu) &=& \frac{b(Pu,Pu)}{c(Pu,Pu)},\\
			&=& \frac{b(Pu,Pu)}{||Pu||^{2}},\\
			&\leq & \frac{\lambda_{m}}{\mu_{m}^{h}}.
	\end{eqnarray*}

@@

Following Lemma \ref{Lem_1}, and since $\lambda_{i}^{h} \geq \lambda_{i}$ it follows that $0 < \mu_{m}^{h} \leq 1$. It is now possible to define the `error bound' in \cite{SF73}:
\begin{eqnarray*}
	\sigma_{m}^{h} = 1 - \mu_{m}^{h}.
\end{eqnarray*}

\newtheorem{Cor_1}{Proposition}
\begin{Cor_1}
	$0 \leq \sigma_{m}^{h} < 1$ and $\lambda_{m}^{h} - \lambda_{m} \leq \lambda_{m}^{h}\sigma_{m}^{h}$
\end{Cor_1}
\begin{proof}
	Starting with the result of Lemma \ref{Lem_1},
	\begin{align*}
		\lambda_{m}^{h} &\leq \frac{\lambda_{m}}{\mu_{m}^{h}} \\
		\lambda_{m}^{h}\mu_{m}^{h} &\leq \lambda_{m} \\
		-\lambda_{m} &\leq -\lambda_{m}^{h}\mu_{m}^{h} \\
		\lambda_{m}^{h} - \lambda_{m} &\leq \lambda_{m}^{h} - \lambda_{m}^{h}\mu_{m}^{h} \\
		\lambda_{m}^{h} - \lambda_{m} &\leq \lambda_{m}^{h}\sigma_{m}^{h}
	\end{align*}
\end{proof}

This result gives an error estimate for the eigenvalues. To prove the convergence of the eigenvalues, it is necessary to prove that the error estimate $\sigma_{m}^{h}$ converges to zero as $h \rightarrow 0$.

\newtheorem{Prop_3}[Prop_1]{Proposition} 
\begin{Prop_3}
	\label{Prop_3}
	$\sigma_{m}^{h} = \max\left\{ 2( u,u-Pu )-||u-Pu||^{2} \ | \ u \in B_{m} \right\}$
\end{Prop_3}
\begin{proof}
	Let $u \in B_{m}$. Then
	\begin{eqnarray*}
		||u - Pu||^{2} &=& c( u - Pu, u - Pu ), \\
						&=& c( u, u ) - 2 c( u, Pu ) + c( Pu, Pu ), \\
						&=& 2c( u, u ) - 2 c( u, Pu ) + c( Pu, Pu ) - c( u, u ),\\
						&=& 2c( u, u - Pu ) + c( Pu, Pu ) - c( u, u ).\\
	\end{eqnarray*}
	consequently
	\begin{eqnarray*}
		c( u, u ) - c( Pu, Pu )  & = & 2c( u, u - Pu ) - ||u - Pu||^{2}.
	\end{eqnarray*}

	Since $u \in B_{m}$, $||u||^{2} = 1$ and hence
	\begin{eqnarray*}
		1 - ||Pu||^{2}  & = & 2c( u, u - Pu ) - ||u - Pu||^{2}.
	\end{eqnarray*}

	On the right hand side, $1 - ||Pu||^{2} \leq 1 - \mu_{m}^{h} = \sigma_{m}^{h}$ for all $u \in B_{m}$. So then it must be that
	\begin{eqnarray*}
	\sigma_{m}^{h} = \max\left\{ 2c( u,u-Pu )-||u-Pu||^{2} \ | \ u \in B_{m} \right \}
	\end{eqnarray*}
\end{proof}

@@

\newtheorem{Prop_4}[Prop_1]{Proposition} 
\begin{Prop_4}
	\label{Prop_4}
	For any $u \in E_{m}$
		\begin{eqnarray*}
		c( u, u - Pu ) = b(u^{*} - Pu^{*}, u -Pu)
		\end{eqnarray*}
\end{Prop_4}
\begin{proof}
	For any $i = 1,2,...,m$,
	\begin{eqnarray*}
	\lambda_{i}c( u_{i},u-Pu ) &=&  b(u_{i}, u-Pu),\\
								&=& b(u_{i}, u-Pu) - b(u-Pu,Pu_{i}) \ \textrm{ (Rayleigh-Ritz Projection)},\\
								&=&  b(u_{i}, u-Pu) - b(Pu_{i},u-Pu),\\
								&=&  b(u_{i}-Pu_{i}, u-Pu).
	\end{eqnarray*}
	Multiplying by $c_{i}\lambda_{i}^{-1}$ and summation over i gives:
	\begin{eqnarray*}
	\sum_{i=1}^{m} c_{i}\lambda_{i}^{-1}\lambda_{i}c( u_{i},u-Pu ) &=& \sum_{i=1}^{m} c_{i}\lambda_{i}^{-1}b(u_{i}-Pu_{i}, u-Pu),\\
								&=& b(\sum_{i=1}^{m} c_{i}\lambda_{i}^{-1}u_{i}-\sum_{i=1}^{m} c_{i}\lambda_{i}^{-1}Pu_{i}, u-Pu),\\
										&=& b(u^{*}-Pu^{*}, u-Pu).
	\end{eqnarray*}
	Therefore $c( u,u-Pu ) = b(u^{*}-Pu^{*}, u-Pu)$.
\end{proof}

\newtheorem{Lem_2}[Lem_1]{Lemma} \label{Lem_2}
\begin{Lem_2}
	$\sigma_{m}^{h} \leq \max \left\{2||u^{*}- Pu^{*}|| ||u-Pu|| \ | \ u \in B_{m} \right\}$
\end{Lem_2}
\begin{proof}
	From Proposition \ref{Prop_3},
	\begin{eqnarray*}
		\sigma_{m}^{h} & = & \max\left\{ 2c( u,u-Pu )-||u-Pu||^{2} \ | \ u \in B_{m} \right\}, \\
					& \leq & \max\left\{ 2c( u,u-Pu ) \ | \ u \in B_{m} \right\}. \\
	\end{eqnarray*}

@@

	From the Approximation Theorem given at the beginning of section \ref{sec:est}, is follows that
	\begin{eqnarray*}
		||u - \Pi u|| \leq Ch^{k}||u^{(k)}||
	\end{eqnarray*}

@@

\newtheorem{Lem_3}[Lem_1]{Lemma} 
\begin{Lem_3}
	\label{Lem_3}
	For any $\epsilon >0$ there exists a $\delta > 0$ such that
	\begin{eqnarray*}
	\sigma_{m}^{h} < \epsilon \ \textrm{ if } \ h < \delta
	\end{eqnarray*}
\end{Lem_3}
\begin{proof}
	For any $\epsilon > 0$ there exists a $\delta > 0$ such that if $h<\delta$, then
	\begin{eqnarray*}
	||u-Pu|| < \epsilon \ \textrm{ for each } \ u \in B_{m}
	\end{eqnarray*}
	This result, together with Lemma \ref{Lem_2} and Proposition \ref{Prop_5} gives the result.
\end{proof}

\newtheorem{Lem_4}[Lem_1]{Lemma} 
\begin{Lem_4}
	\label{Lem_4}
	There exists a $\delta > 0$ such that for $h < \delta$
	\begin{eqnarray*}
	\lambda_{m}^{h} - \lambda_{m} \leq 2\lambda_{m}\sigma_{m}^{h}
	\end{eqnarray*}
\end{Lem_4}
\begin{proof}
	Using Lemma \ref{Lem_3}, choose $\delta$ such that $\sigma_{m}^{h} < \frac{1}{2}$. Then by Lemma \ref{Lem_1} gives that $\lambda_{m}^{h} < 2\lambda_{m}$.\\

 	Therefore $\lambda_{m}^{h} - \lambda_{m} \leq 2\lambda_{m}\sigma_{m}^{h}$.
\end{proof}

@@

\newtheorem{Lem_5}[Lem_1]{Lemma} \label{Lem_5}
\begin{Lem_5}
	\begin{eqnarray*}
		b(u_{m}-u_{m}^{h},u_{m}-u_{m}^{h}) &=& \lambda_{m}c( u_{m}-u_{m}^{h},u_{m}-u_{m}^{h} ) + \lambda_{m}^{h} - \lambda_{m}
		\end{eqnarray*}
\end{Lem_5}
\begin{proof}
	\begin{eqnarray*}
		b(u_{m}-u_{m}^{h},u_{m}-u_{m}^{h}) &=& b(u_{m},u_{m}) - 2b(u_{m},u^{h}_{m}) + b(u^{h}_{m},u^{h}_{m}) \\
										&=& \lambda_{m} c( u_{m}, u_{m} ) - 2\lambda_{m} c( u_{m}, u^{h}_{m} ) + \lambda_{m}^{h}c( u_{m}^{h},u_{m}^{h} )\\
										&=&  \lambda_{m} - 2\lambda_{m} c( u_{m}, u^{h}_{m} ) + \lambda_{m}^{h} \\
										&=& 2\lambda_{m} - 2\lambda_{m} c( u_{m}, u^{h}_{m} ) + \lambda_{m}^{h} - \lambda_{m}\\
										&=& \lambda_{m}c( u_{m}-u_{m}^{h},u_{m}-u_{m}^{h}) + \lambda_{m}^{h} - \lambda_{m}
		\end{eqnarray*}
\end{proof}

It has been shown that the eigenvalues converge to the exact eigenvalues as $h \rightarrow 0$. So from this result, it only remains to show that $c( u_{m}-u_{m}^{h},u_{m}-u_{m}^{h}) \rightarrow 0$ as $h \rightarrow 0$.

@@

\newtheorem{Lem_6}[Lem_1]{Lemma} \label{Lem_6}
\begin{Lem_6}
	For all m and j
	\begin{eqnarray*}
	(\lambda_{j}^{h} - \lambda_{m}) c( Pu_{m}, u_{j}^{h}) = \lambda_{m} c( u_{m}-Pu_{m},u_{j}^{h} )
	\end{eqnarray*}
\end{Lem_6}
\begin{proof}
	Since the term $\lambda_{m}c( Pu,u^{h}_{j})$ appears on both sides of the equation, it is only required to show that
	\begin{eqnarray*}
		\lambda_{j}^{h}c( Pu, u_{j}^{h} ) &=& \lambda_{m} c( u, u_{j}^{h} ).	
	\end{eqnarray*}
	Since both $u$ and $u_{j}^{h}$ are eigenfunctions, then
	\begin{eqnarray*}
		\lambda_{j}^{h}c( Pu, u_{j}^{h} ) &=& b(Pu,u_{j}^{h})\\
		\lambda_{m} c( u, u_{j}^{h} ) &=& b(u,u_{j}^{h})
	\end{eqnarray*}

@@

The set $\left\{u_{1}^{h},u_{2}^{h},...,u_{N}^{h}\right\}$ forms an orthonormal basis for $S^{h}$. The projection $Pu_{m}$ can be written as:
\begin{eqnarray}
	Pu_{m} &=& \sum_{j=1}^{N} c( P u_{m} ,u_{j}^{h}) u_{j}^{h}. \label{CV1}
\end{eqnarray}

From Lemma \ref{Lem_6}, it follows that $c( P_{m},u_{j}^{h} )$ is small if $\lambda_{m}^{h}$ is not close to $\lambda_{j}$. Therefore (\ref{CV1}) tells us that $Pu_{m}$ is close to $u_{m}^{h}$. The estimate for $Pu_{m} - u_{m}^{h}$ will follow from this result.

@@

To simplify the notation, let $\beta = c(Pu_m,Pu_m^h)$.

@@

Using Lemma \ref{Lem_6}:
\begin{eqnarray*}
||Pu - \beta u_{m}^{h}||^{2} &=& \sum_{j\neq m} \left(\frac{\lambda_{m}}{|\lambda_{m} - \lambda_{j}^{h}|}\right)^{2} c( u_{m} - Pu_{m} ,u_{j}^{h})^{2},\\
				&\leq & \rho^{2} \sum_{j\neq m} c( u_{m} - Pu_{m} ,u_{j}^{h})^{2}, \\
				&\leq & \rho^{2} \sum_{j=1}^{N} c( u_{m} - Pu_{m} ,u_{j}^{h})^{2}, \\
				& = & \rho^{2} ||u_m - Pu_m||^{2}.\\
\end{eqnarray*}
\end{proof}
\end{comment}
